---
title: "Exploratory Analysis of BC (Black Carbon) for mobile monitoring"
author: "Adithi R. Upadhya - ILK Labs"
date: "7/11/2020"
output: 
  html_document:
    df_print: paged
    fig_width: 8
    fig_height: 6
    toc: true
    code_folding: hide
    css: style_bc.css
    toc_float: true
    number_sections: true
    fig_caption: true
theme: yeti
---


```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
library(lubridate)
library(stringr)
library(ggrepel)
f <- function(x) {
  r <- quantile(x, probs = c(0.05, 0.25, 0.5, 0.75, 0.95))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}
completeFun <- function(data, desiredCols) {
    completeVec <- complete.cases(data[, desiredCols])
    return(data[completeVec, ])
  }
```



```{r include = FALSE, warning = FALSE, message = FALSE}
setwd("D:/Dropbox/APMfull/All_Data_CNG_Dsl/Joined_files")
dir <- "D:/Dropbox/APMfull/All_Data_CNG_Dsl/Joined_files"
shp_list <- list.files(dir, pattern = "\\.csv$")
all_data <- data.frame()
for (each_file in (shp_list)) {
  df <- read.csv(each_file, header = TRUE, sep = ",")
  df <- data.frame(df)
  df$Atmos <- NULL
  df$file <- stringr::str_extract(each_file, "[0-9]{4}\\_[0-9]{2}\\_[0-9]{2}")
  start_date <- as.POSIXct(df[1, "date"], format = "%Y-%m-%d %H:%M:%S", 
                            tz ="Asia/Kolkata")
  if (is.na(start_date)) {
    start_date <- as.POSIXct(df$date, format = "%d-%m-%Y %H:%M", 
                            tz ="Asia/Kolkata")
    if (is.na(start_date)) {
      df$date <- as.POSIXct(df$date, format = "%m/%d/%Y %H:%M", 
                            tz ="Asia/Kolkata")
    } else {
      df$date <- as.POSIXct(df$date, format = "%d-%m-%Y %H:%M", 
                            tz ="Asia/Kolkata")
    }
  } else {
    df$date <- as.POSIXct(df$date, format = "%Y-%m-%d %H:%M:%S", 
                            tz ="Asia/Kolkata")
  }
  df$Area <- substr(each_file, 20, 23)
  df$Area <- gsub("_", "", df$Area)
  all_data <- rbind(all_data, df)
}
all_data <-completeFun(all_data, c("Latitude"))
all_data$day <- as.Date(all_data$date, format = '%Y-%m-%d', tz = "Asia/Kolkata")
all_data$month <- as.Date(all_data$date, format = '%Y-%m-%d', tz = "Asia/Kolkata")
```


# Mobile Monitoring report

**The mobile monitoring campaign started in May 2019 with Diesel car, while the monitoring continued with CNG car from 09 July 2019.**

**All rides are included (CNG + Diesel).**

```{r}
all_data_summary <- all_data %>%
  dplyr::select(BC)
summ <- summary(all_data_summary)
summ <- data.frame(summ)
summ$Var1 <- NULL
names(summ) <- c("Parameter", "Stats")
summ
```


# Data Availability of Black Carbon during mobile monitoring campaign (2019 - 2020)

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 1: Data availability of BC for all rides"}
all_data_BC <- all_data %>%
  dplyr::select(day, BC) %>%
        group_by(day) %>%
        summarise_all(funs(mean, sd, median, IQR), na.rm = TRUE)
names(all_data_BC) <- c("date", "BC_mean", "BC_sd", "BC_median", "BC_IQR")
no_na_df <- data.frame(all_data_BC$date, all_data_BC$BC_mean)
names(no_na_df) <- c("date", "BC")
no_na_df <- no_na_df[complete.cases(no_na_df), ]
no_na_df$Exp <- "Mobile Monitoring Data"
y <- ggplot(no_na_df, aes(x = date, y = Exp)) + 
  geom_errorbarh(aes(xmax = date, xmin = date), size = 0.7, colour = "steelblue") + 
  labs(x = "", y = "Mobile Monitoring Data") +
  scale_x_date(date_labels ="%b", date_breaks = "1 month") +
  theme_classic() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1), 
        legend.position = "none",
        strip.background = element_blank(), strip.text = element_blank())
y
```

# Monthly Box Plot for Diesel and CNG Car

**The data used here is (loading corrected) BC which is aggregrated over snapped 30 m road segment and plotted for each month.**

```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 2: Monthly box plots of BC for all rides"}
all_data$month <- format(all_data$date, "%Y-%m-01 01:00:00")
all_data$month <- as.POSIXct(all_data$month, format = '%Y-%m-%d %H:%M:%S', 
                             tz = "Asia/Kolkata")
plot_box <- ggplot(all_data, aes(x = reorder(format(all_data$date, '%b'), 
                                             all_data$date), y = BC)) + 
  labs(title = "Monthly box plot", x = "", y = expression(paste(BC, "(", mu, 
                                                                "g", ~ m^{-3}, ")"))) + geom_rect(data = all_data, aes(xmin = "Jul", xmax = "Jul", ymin = -Inf, ymax = Inf), colour = "red", fill = "red") +
  stat_summary(fun.data = f, geom ="boxplot", width = 0.7, size = 0.5) +  
  stat_summary(fun.y = mean, geom = "point", size = 1) +
  scale_y_continuous(limits = c(0, 200)) + theme_classic() +
  theme(legend.text = element_text(size = 14),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size = 18, colour = "black", face = "bold"), 
        axis.text = element_text(size = 16, colour = "black", face ="bold"),
        axis.text.x = element_text(size = 14, colour = "black", face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1)) + annotate(geom = "text", label = "Diesel", x = "Jun", y = 170, size = 6) + annotate(geom = "text", label = "CNG", x = "Aug", y = 170, size = 6) 
plot_box
```


# Daily Summary Statistics for Black Carbon

__**Note:Transition from Diesel to CNG on 09 July 2019.**__

```{r fig.align = "center", warning = FALSE, message = FALSE, rows.print = 10}
all_data_BC <- all_data %>%
  dplyr::select(day, Area, BC) %>%
        group_by(day, Area) %>%
        summarise_all(funs(mean, sd, median, IQR), na.rm = TRUE)
columns_of_interest <- 3:ncol(all_data_BC)
all_data_BC[ , columns_of_interest] <- sapply(X = all_data_BC[ , columns_of_interest], FUN = function(x) round(x, digits = 2))
names(all_data_BC) <- c("date", "Area", "BC_mean", "BC_sd", "BC_median", "BC_IQR")
all_data_BC
```

## t-test to check for passes in CNG and Diesel.

**Daily mean calculated using the individual aggregated 30 m road segment data in each area. Here we used the daily mean of (loading corrected) BC to apply t-test for all the 4 (CBD + Kannur + Malleshwaram 1 + Malleshwaram 2) areas together.**

```{r message = FALSE, warning = FALSE}
all_data_BC_Dsl <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date <= "2019-07-08")
names(all_data_BC_Dsl) <- c("date", "Area", "BC_Dsl")
all_data_BC_CNG <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date >= "2019-07-09")
names(all_data_BC_CNG) <- c("date", "Area", "BC_CNG")
t_test <- t.test(all_data_BC_CNG$BC_CNG, all_data_BC_Dsl$BC_Dsl)
t_test
```

**Here we used the daily mean of (loading corrected) BC to apply t-test for CBD CNG and Diesel data.**

```{r message = FALSE, warning = FALSE}
CBD_BC_Dsl <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date <= "2019-07-08") %>%
  filter(Area == "CBD")
names(CBD_BC_Dsl) <- c("date", "Area", "BC_Dsl")
CBD_BC_CNG <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date >= "2019-07-09") %>%
  filter(Area == "CBD")
names(CBD_BC_CNG) <- c("date", "Area", "BC_CNG")
t_test <- t.test(CBD_BC_CNG$BC_CNG, CBD_BC_Dsl$BC_Dsl)
t_test
```

**Here we used the daily mean of (loading corrected) BC to apply t-test for Kannuru CNG and Diesel data.**

```{r message = FALSE, warning = FALSE}
KAN_BC_Dsl <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date <= "2019-07-08") %>%
  filter(Area == "KAN")
names(KAN_BC_Dsl) <- c("date", "Area", "BC_Dsl")
KAN_BC_CNG <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date >= "2019-07-09") %>%
  filter(Area == "KAN")
names(KAN_BC_CNG) <- c("date", "Area", "BC_CNG")
t_test <- t.test(KAN_BC_CNG$BC_CNG, KAN_BC_Dsl$BC_Dsl)
t_test
```

**Here we used the daily mean of (loading corrected) BC to apply t-test for Malleshwaram 1 CNG and Diesel data.**

```{r message = FALSE, warning = FALSE}
MAL1_BC_Dsl <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date <= "2019-07-08") %>%
  filter(Area == "MAL1")
names(MAL1_BC_Dsl) <- c("date", "Area", "BC_Dsl")
MAL1_BC_CNG <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date >= "2019-07-09") %>%
  filter(Area == "MAL1")
names(MAL1_BC_CNG) <- c("date", "Area", "BC_CNG")
t_test <- t.test(MAL1_BC_CNG$BC_CNG, MAL1_BC_Dsl$BC_Dsl)
t_test
```

**Here we used the daily mean of (loading corrected) BC to apply t-test for Malleshwaram 2 CNG and Diesel data.**

```{r message = FALSE, warning = FALSE}
MAL2_BC_Dsl <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date <= "2019-07-08") %>%
  filter(Area == "MAL2")
names(MAL2_BC_Dsl) <- c("date", "Area", "BC_Dsl")
MAL2_BC_CNG <- all_data_BC %>%
  dplyr::select(date, Area, BC_mean) %>%
  filter(date >= "2019-07-09") %>%
  filter(Area == "MAL2")
names(MAL2_BC_CNG) <- c("date", "Area", "BC_CNG")
t_test <- t.test(MAL2_BC_CNG$BC_CNG, MAL2_BC_Dsl$BC_Dsl)
t_test
```


# Monthly Diurnal variation of BC using BCc channel of AE33

```{r warning = FALSE, message = FALSE, include = FALSE}
setwd("D:/Dropbox/APMfull/Colocation CSTEP/CSTEP_co-location_2020/Exp_9_2020_01_15/AE33_CSTEP")
ae33_cstep <- data.frame()
dir <- "D:/Dropbox/APMfull/Colocation CSTEP/CSTEP_co-location_2020/Exp_9_2020_01_15/AE33_CSTEP/"
shp_list1 <- list.files(dir, pattern = "\\.dat$")
for (fil in (shp_list1)) {
  ae33_1 <- read.table(paste("D:/Dropbox/APMfull/Colocation CSTEP/CSTEP_co-location_2020/Exp_9_2020_01_15/AE33_CSTEP/", fil, sep = ""), header = TRUE, skip = 4)
  ae33_1 <- data.frame(ae33_1)
  ae33_1$date <- with(ae33_1, as.POSIXct(paste(as.Date(Date.yyyy.MM.dd.., format = "%Y/%m/%d"), Time.hh.mm.ss..)))
 ae33_1$BC6. <- ae33_1$BC6. / 1000
 ae33_1$BC1. <- ae33_1$BC1. / 1000
 ae33_1 <- ae33_1[ae33_1$Status. == 0 || ae33_1$Status. == 256 || ae33_1$Status. == 128, ]
 ae33_1 <- dplyr::select(ae33_1, date,BC6., BC1.)
 ae33_cstep <- rbind(ae33_cstep, ae33_1)
}
names(ae33_cstep) <- c("date", "AE33_cstep", "UVPM_cstep")


Final <- data.frame(ae33_cstep)
Final <- Final[Final$AE33_cstep > 0.000, ]
Final <- Final[Final$UVPM_cstep > 0.000, ]
Final$month <- format(Final$date, "%m")
Final$hour1 <- lubridate::ceiling_date(Final$date, "hour")
Final$Date<- as.Date(as.POSIXct(Final$date, tz = "Asia/Kolkata"), tz = "Asia/Kolkata")
Final <- Final[Final$Date != "2019-08-13", ]
Final <- Final[Final$Date != "2019-08-14", ]
Final <- Final[Final$Date != "2019-08-18", ]
Final <- Final[Final$Date != "2019-08-19", ]
Final <- Final[Final$Date != "2019-08-20", ]
Final <- Final[Final$Date != "2019-08-21", ]
Final <- Final[Final$Date != "2019-08-30", ]
Final <- Final[Final$Date != "2019-08-31", ]
Final <- Final[Final$Date != "2019-09-01", ]
Final <- Final[Final$Date != "2019-09-02", ]
Final1 <- Final %>%
  dplyr::select(hour1, AE33_cstep) %>%
  group_by(hour1)%>%
  summarise(mean_AE33_cstep = mean(AE33_cstep, na.rm = TRUE))

Final1$hour  <- format(Final1$hour1, "%H")
Final1$month <- format(Final1$hour1, "%m")
Final1$hourt <- as.numeric(as.character(Final1$hour))


Final7 <- Final1[Final1$month == "07", ]
Final7$month <- as.numeric(as.character(Final7$month))

Final7 <- Final7 %>%
  dplyr::select(hour, month, mean_AE33_cstep) %>%
  group_by(hour) %>%
  summarise_all(funs(median), na.rm = TRUE)


Final8 <- Final1[Final1$month == "08", ]
Final8$month <- as.numeric(as.character(Final8$month))

Final8 <- Final8 %>%
  dplyr::select(hour, month, mean_AE33_cstep) %>%
  group_by(hour) %>%
  summarise_all(funs(median), na.rm = TRUE)


Final9 <- Final1[Final1$month == "09", ]
Final9$month <- as.numeric(as.character(Final9$month))

Final9 <- Final9 %>%
  dplyr::select(hour, month, mean_AE33_cstep) %>%
  group_by(hour) %>%
  summarise_all(funs(median), na.rm = TRUE)

Final10 <- Final1[Final1$month == "10", ]
Final10$month <- as.numeric(as.character(Final10$month))

Final10 <- Final10 %>%
  dplyr::select(hour, month, mean_AE33_cstep) %>%
  group_by(hour) %>%
  summarise_all(funs(median), na.rm = TRUE)

Final11 <- Final1[Final1$month == "11", ]
Final11$month <- as.numeric(as.character(Final11$month))

Final11 <- Final11 %>%
  dplyr::select(hour, month, mean_AE33_cstep)%>%
  group_by(hour) %>%
  summarise_all(funs(median), na.rm = TRUE)


Final12 <- Final1[Final1$month == "12", ]
Final12$month <- as.numeric(as.character(Final12$month))

Final12 <- Final12 %>%
  dplyr::select(hour, month, mean_AE33_cstep) %>%
  group_by(hour) %>%
  summarise_all(funs(median), na.rm = TRUE)

Final01 <- Final1[Final1$month == "01", ]
Final01$month <- as.numeric(as.character(Final01$month))

Final01 <- Final01 %>%
  dplyr::select(hour, month, mean_AE33_cstep) %>%
  group_by(hour) %>%
  summarise_all(funs(median), na.rm = TRUE)

Final02 <- Final1[Final1$month == "02", ]
Final02$month <- as.numeric(as.character(Final02$month))

Final02 <- Final02 %>%
  dplyr::select(hour, month, mean_AE33_cstep) %>%
  group_by(hour) %>%
  summarise_all(funs(median), na.rm = TRUE)

Final7$month <- str_replace(Final7$month, '7', 'Jul-2019')
Final8$month <- str_replace(Final8$month, '8', 'Aug-2019')
Final9$month <- str_replace(Final9$month, '9', 'Sep-2019')
Final10$month <- str_replace(Final10$month, '10', 'Oct-2019')
Final11$month <- str_replace(Final11$month, '11', 'Nov-2019')
Final12$month <- str_replace(Final12$month, '12', 'Dec-2019')
Final01$month <- str_replace(Final01$month, '1', 'Jan-2020')
Final02$month <- str_replace(Final02$month, '2', 'Feb-2020')

Final_c <- rbind(Final7, Final8, Final9, Final10, Final11, Final12, Final01, Final02)

# Final_c$month<-format(as.POSIXct(Final_c$month, format="%m"), format="%m")
```


```{r fig.align = "center", warning = FALSE, message = FALSE, fig.cap = "\\label{fig:figs}Fig 3: Monthly diurnal variation from AE33"}
Final_cq <- Final_c
Final_cq$size_f <- factor(Final_cq$month, levels = c('Jul-2019', 'Aug-2019', 'Sep-2019', 'Oct-2019', 'Nov-2019', 'Dec-2019', 'Jan-2020', 'Feb-2020'))
min_m <- data.frame(Final_cq)
min_m$hour <- format(as.POSIXct(min_m$hour, format = "%H"), format = "%H:%M:%S")
min_m$hour <- as.POSIXct(paste0("2016-09-23 ", min_m$hour), tz = "Asia/Kolkata")
min_m$mean_AE33_cstep <- as.numeric(as.character(min_m$mean_AE33_cstep))
ae33_line <- ggplot(data = min_m, aes(hour, mean_AE33_cstep)) + 
  geom_line(size =  0.9) + theme_minimal() + 
  scale_x_datetime(date_labels = "%H") + facet_wrap(~ size_f, nrow = 2) +
  labs(y = expression(paste(BCc, " (", mu, "g", ~m^{-3}, ")")), x = "") + scale_y_continuous() + 
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 14),
        plot.title = element_text(size = 12, face = "bold"),
        plot.subtitle = element_text(size = 10, face = "bold"), 
        axis.title = element_text(size=14), 
        axis.text = element_text(size = 12, face = "bold"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1))
ae33_line 

```

